---
title: "Assignment5"
author: "John Dreyfous"
date: "1/19/2023"
output: html_document
---
## Question 2

a. 
```{r}
my_matrix <- matrix(data= runif(16), nrow=4)
print(my_matrix)
```
b. 
```{r}
my_logical <- runif(100) > 0.5
print(my_logical)
```
c. 
```{r}
my_letters <- sample(letters)
print(my_letters)
```
d. create a new list, which has the element[2,2] from the matrix, the second element of the logical vector, and the second element of
```{r}
list1 <- list(my_matrix[2,2], my_logical[2], my_letters[2])
print(list1)
```
e. 
```{r}
print(typeof(list1))
print(str(list1))
```
f. combine the underlying elements from the new list into a single atomic vector with the c() function.
what is the data type of this vector?
```{r}
list2<-c(my_matrix[2,2], my_logical[2], my_letters[2])
typeof(list2)
print(typeof(list2))
```

## Question 3: Create an empty data frame with two variables (= columns) and 26 observations (= rows) below:
```{r}
VarA <- 1:26
VarB <- 1:26
dFram <- data.frame(VarA, VarB, stringsAsFactors = F)
dFram[dFram>0] <- NA
print(dFram)
```


a/b. call the first column/variable my_unifs and fill it with 26 random uniform values from 0 to 10

```{r}
my_unifs <- runif(26, 0, 10)
my_letters <- sample(LETTERS)
dFram <- data.frame(my_unifs, my_letters, stringsAsFactors = F)
print(dFram)
```
c. 
```{r}
my_unifs <- runif(26, 0, 10)
my_letters <- sample(LETTERS)
dFram <- data.frame(my_unifs, my_letters, stringsAsFactors = F)
dFram[sample(nrow(dFram), 4),1] <- NA
print(dFram)
```
d. 
```{r}
which(is.na(dFram[,1]))
print(which(is.na(dFram[,1])))
```
e. 
```{r}
orderFram <- dFram[order(dFram$my_letters),] 
print(orderFram)
```
f. 
```{r}
dFram <- data.frame(my_unifs, my_letters, stringsAsFactors = F)
mean(dFram[ , 1])
print(mean(dFram[ , 1]))
```
g. 
```{r}
my_LETTERS <- sample(LETTERS)
dFram <- data.frame(my_unifs, my_LETTERS, stringsAsFactors = F)
print(dFram)
```

