---
title: "Assignment9"
author: "John Dreyfous"
date: "1/30/2023"
output: html_document
---

##### 1.Using a for loop and an if statement, write a function to calculate the number of zeroes in a numeric vector. Before entering the loop, set up a vector of integers with some zero values. Then, set up a counter variable counter <- 0. Inside the loop, add 1 to counter each time you have a zero in the vector. Finally, use return(counter) for the output.

```{r}
 Vec<-sample(rep(0:1, times=4))
z<-0
newVec<- function(vector){for(i in 1:length(Vec)){
  if(Vec[i]==0){z<-z+1}
}
return(z)
}
newVec(Vec)
```


##### 2. Write a function that takes as input two integers representing the number of rows and columns in a matrix. The output is a matrix of these dimensions in which each element is the product of the row number x the column number.
```{r}
m<- function(rows, columns){
  mat<- matrix(data=NA, nrow=rows, ncol = columns) 
  for(i in 1:rows){
  for(j in 1:columns){
    mat[i,j]<- (i*j)
  }
  }
  return(mat)
    }
m(rows=6, columns=4)
```


##### 3. Use a for loop to repeat your previous functions from Weekly Assignment 2 (which simulate a data frame and extract a p-value) 100 times. Store the results in a data frame that has 1 column indicating the replicate number and 1 column for the p-values (a total of 2 columns and 100 rows).


```{r}
### Replicate data frame
Q1<-function(Type=NULL, Value=NULL){
  Type <- 1:50
  Value <- 1:50
  dataFrame <- data.frame(Type, Value, stringsAsFactors = F)
  dataFrame[1:25,1] <- "Control"
  dataFrame[26:50, 1] <- "Treatment"
  dataFrame[1:25,2] <- rnorm(n=25, mean=10, sd=1.5)
  dataFrame[26:50,2] <- rnorm(n=25, mean=45, sd=2)
  return(dataFrame)
}
daFrame<-Q1()

### Return p-value
pvalF <- function(d = NULL){
  table = summary(aov(d[[2]] ~ d[[1]], data = d))
  p <- table[[1]][["Pr(>F)"]][[1]]
  return(p)
}
```
```{r}
### Create Pval function using for loop

repPval <- function(replicates=1:100, rows = NULL){
  replicates<-1:100
  rows<-1:100
  finalFrame <- data.frame(replicates=1:100, y=rows)
  colnames(finalFrame) <- c("p-values", "replicates")
  for(i in rows){
   finalFrame[i,] <- pvalF(Q1())
  }
  finalFrame[1:100, 2]<- 1:100
  return(finalFrame)
}
repPval()
```


