---
title: "Assignment4"
author: "John Dreyfous"
date: "1/17/2023"
output: html_document
---
## Question 1
##### Assign to the variable n_dims a single random integer between 3 and 10.
```{r}
n_dims<-sample(3:10, 1)
print(n_dims)
```

#### Create a vector of consecutive integers from 1 to n_dims^2.
```{r}
vector <- 1:(n_dims)^2
print(vector)
```
##### Use the sample function to randomly reshuffle these values.
```{r}
rearrange<-sample(vector)
```
#####create a square matrix with these elements.
```{r}
sMat<- matrix(data=rearrange, nrow=n_dims)
print(sMat)
```
 #####  print out the matrix.^^^ 


 #####  find a function in r to transpose the matrix.
```{r}
Tran_sMat <- t(sMat)
print(Tran_sMat)
```

  ##### print it out again and note how it has changed.

 ##### calculate the sum and the mean of the elements in the first row and then the last row.
```{r}
sumFirst<-sum(Tran_sMat[1,])
meanFirst<-mean(Tran_sMat[1,])
sumLast<-sum(Tran_sMat[n_dims,])
meanLast<-mean(Tran_sMat[n_dims,])
print(sumFirst)
print(meanFirst)
print(sumLast)
print(meanLast)
```
 

 ##### set your code up so you can re-run it to create a matrix of a different size by only changing the n_dims value
 




