---
title: "Weekly Assignment 3"
author: "John Dreyfous"
date: "1/29/2023"
output: html_document
---

### Question 1: Go to Dryad to choose a published paper and data set and reconstruct your own figure. Code a ggplot graph that looks as close to the published figure as you can.

#### Model Figure and Citation
![Fig 11. Effect of migration date on acute DD20 accumulation.
Relationships between release date and the accumulation of acute temperature exposure measured in degree days ≥20 °C (DD20) for individual fall Chinook salmon (n = 21, blue symbols) and steelhead (n = 75, gold symbols) during their ~470 rkm migration from release to Lower Granite Dam in 2000 and 2002.   ](https://raw.githubusercontent.com/jdreyfous/BIOL1007A/main/Figure_For_WA3.png)

**Data Citation:** Keefer, Matthew L. et al. (2019), Data from: Thermal exposure of adult Chinook salmon and steelhead: diverse behavioral strategies in a large and warming river system, Dryad, Dataset, https://doi.org/10.5061/dryad.gc632bc

**Article Citation:** Keefer, M. L., Clabough, T. S., Jepson, M. A., Johnson, E. L., Peery, C. A., & Caudill, C. C. (2018). Thermal exposure of adult Chinook salmon and steelhead: Diverse behavioral strategies in a large and warming river system. PLOS ONE, 13(9), e0204274. https://doi.org/10.1371/journal.pone.0204274

### Figure Replication

##### Metadata
```{r}
### Reaches 1-8	= summary data for the full study reach
### SPECIES: SPP 	= species (ASH = steelhead, FA= fall Chinooks salmon, SP = spring Chinook salmon, SU = summer Chinook salmon)
### RELEASE DATE (RD): tagdate	= date fish was tagged
### WATER TEMP ON RD: WQM T on tagdate = Columbia River water temperature on the date fish was tagged
### T mean	= mean fish temperature
### T std	= standard deviation of fish temperature
### T max	= maximum fish temperature
### T min	= minimum fish temperature
```
```{r}
library(tidyverse)
library(ggthemes)
library(dplyr)
```
```{r}
fishData <- read_csv("WA3_Figure_Data.csv")
bySpecies<- fishData %>% 
  group_by(SPP) %>% 
  summarize(DDT20, julian, TotalNumber=n())%>% 
  filter(DDT20>=0)
  SteelFa<-filter(bySpecies, TotalNumber>199 | TotalNumber<29 & julian>151)
p<-ggplot(data = SteelFa, mapping=aes(x = julian, y= DDT20, color=SPP, na.rm=T))+
  geom_point(size=2.5, show.legend = F)+
  xlab("Relase Date")+
  ylab("Degree days >20C")+ 
  ylim(1,25)+
  scale_y_continuous(breaks=c(0, 5, 10, 15, 20, 25, 30))+
  scale_color_manual(values=c("ASH"="darkolivegreen4", "FA"="blue")) + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))
 p
```

### QUESTION 2: Perform a simple analysis (linear regression, ANOVA, t-test, chi-squared, or logistic regression) using two variables from the data set. Print the analysis’ summary table.

```{r}
Anova<- aov(DDT20~julian, data = SteelFa, projections = T, qr = T, contrasts = NULL)
summary(Anova)
```




